\section{Blocked Gibbs Algorithm}

One Gibbs sweep for the Gaussian NDLM proceeds as follows.
Each step is evaluated from the computable kernels in
\eqref{eq:log_joint_A}--\eqref{eq:log_joint_C} and the conditional families in
\eqref{eq:cond_sigma} and \eqref{eq:cond_W_fcast}.
Because $\lambda$ is fixed, there is no separate update for the transfer rate.
If the unified A+B+C model is fit jointly, the forecast block is anchored by the deterministic
bridge \eqref{eq:fcast_bridge}; if standalone Model C is fit conditionally, replace that bridge by
the external Gaussian anchor from Section~1.

\begin{enumerate}[label=\textbf{Step \arabic*:},leftmargin=2.8cm]
\item Sample state trajectories using FFBS:
\begin{align*}
\bm x_{t_0:t_1}^{(s)} \sim p(\bm x_{t_0:t_1}\given\text{data},\Theta^{(s-1)}),
\end{align*}
with block choice either joint stacked state or conditional blocks.
Historical blocks use the known time-varying discount-induced covariances
$\tilde{\bm W}_t$ and $\bm W_t^{\delta^j}$.
If Model C is active, the forecast FFBS block is run on
$\bm x_{T:T+K_{\max}}^{(f)}$ using the current lead-specific
$\{\bm W_{T+k}^{(f)}\}_{k=1}^{K_{\max}}$ and the reduced or augmented state specification selected
in Section~1.

\item Update observation variances for each source $j$ using \eqref{eq:cond_sigma}.

\item Update each forecast lead-specific covariance
$\bm W_{T+k}^{(f)}$ independently using \eqref{eq:cond_W_fcast}.
\end{enumerate}

\subsection{One-sweep pseudocode with required intermediates}
\begin{enumerate}[label=\textbf{P\arabic*:},leftmargin=2.0cm]
\item Build source-wise residual sums of squares using \eqref{eq:joint_residuals}
and current state draws:
\[
\mathrm{SSE}_j=\sum_{n\in\mathcal{I}_j}\big(r_n^{(j)}\big)^2.
\]
\item Draw state paths by FFBS with \eqref{eq:kf_f}--\eqref{eq:ffbs_cond},
assimilating all observations at each time in observation-list order.
\item If the unified A+B+C model is used, enforce the deterministic forecast initial condition
$\bm x_T^{(f)}=\bm H_T^{(f)}(\bm\alpha_T,\bm\delta_T^{1:J_f})$ before propagating the forecast FFBS
block.
\item Draw each $\sigma_j^2$ from \eqref{eq:cond_sigma} using the updated $\mathrm{SSE}_j$.
\item For each forecast lead $k$, compute
$\bm u_{T+k}^{(f)}(\bm u_{T+k}^{(f)})^\T$ from \eqref{eq:fcast_innovation}
and draw $\bm W_{T+k}^{(f)}$ from \eqref{eq:cond_W_fcast}.
\end{enumerate}
Practical numerics: use Cholesky solves for Kalman/FFBS covariance systems and symmetrize sampled
covariance matrices before reuse in the next sweep.

\subsection{Diagnostics Required for Correctness}
Track and report:
\begin{itemize}
\item Effective sample size and trace stability for each $\sigma_j^2$ and for representative
      scalar summaries of $\bm W_{T+k}^{(f)}$ (for example, diagonal entries or log-determinants).
\item Historical innovation quadratic forms using the known discount-induced covariances, namely
      $(\bm e_t^A)^\T\tilde{\bm W}_t^{-1}\bm e_t^A$ and
      $(\bm e_t^{\delta,j})^\T(\bm W_t^{\delta^j})^{-1}\bm e_t^{\delta,j}$, and forecast innovation quadratic forms
      $(\bm u_{T+k}^{(f)})^\T(\bm W_{T+k}^{(f)})^{-1}\bm u_{T+k}^{(f)}$.
\item Posterior predictive calibration at historical holdout points.
\end{itemize}
Because each $\bm W_{T+k}^{(f)}$ is informed by a single transition innovation, its posterior can be
substantially prior-dominated; this is an exact consequence of the model, not a heuristic approximation.
