\section{Mean-Field Variational Bayes (CAVI)}

\subsection{Factorization}
Use
\begin{align}
q(\text{states},\sigma^2,W^{(f)})
= q(\text{states})\prod_{j=0}^J q(\sigma_j^2)
\prod_{k=1}^{K_{\max}} q(\bm W_{T+k}^{(f)}),
\label{eq:vb_factorization}
\end{align}
where the historical evolution covariances are deterministic discount-factor-defined inputs rather
than latent random variables. Because $\lambda$ is fixed, no variational factor is introduced for it.
Each coordinate update uses the generic CAVI rule
\begin{align}
\log q_i^\star(\vartheta_i)
= \E_{q_{-i}}[\log p(\text{data},\text{all unknowns})] + \text{const},
\label{eq:vb_cavi_rule}
\end{align}
then identifies the corresponding exponential-family kernel.

\subsection{State Factor}
Given current expected precisions,
\begin{align}
q(\text{states})\propto
\exp\Big(\E_{-\text{states}}[\log p(\text{data},\text{states},\sigma^2,W^{(f)})]\Big),
\end{align}
which remains Gaussian and is computed by a Kalman smoother on a pseudo-model with
$\E_q[1/\sigma_j^2]$ inserted in the observation precisions.
In the unified A+B+C model, the state factor is additionally constrained by the deterministic
bridge \eqref{eq:fcast_bridge}; equivalently, the forecast block may be smoothed conditionally on
the terminal historical state.
For historical Model A/B transitions, use the known time-varying discount-induced covariances
$\tilde{\bm W}_t$ and $\bm W_t^{\delta^j}$ directly.
For forecast transitions, each lead $T+k$ uses its own expected precision
\begin{align}
\bm P_{T+k}^{(f)}:=\E_q[(\bm W_{T+k}^{(f)})^{-1}],
\label{eq:vb_forecast_precision}
\end{align}
so the forecast pseudo-transition is time-varying even when the forecast state dimension is fixed.
In covariance-form recursions, it is convenient to define the derived pseudo-covariance
\begin{align}
\bar{\bm W}_{T+k}^{(f)} := (\bm P_{T+k}^{(f)})^{-1},
\end{align}
but this quantity is \emph{not} $\E_q[\bm W_{T+k}^{(f)}]$.
This is the direct Gaussian kernel implied by \eqref{eq:vb_cavi_rule} and
\eqref{eq:log_joint_A}--\eqref{eq:log_joint_C}: known historical covariances in the historical
window, and expected inverse lead-specific forecast covariances in the forecast window.

\subsection{Variance Factors}
For each $j$,
\begin{align}
q(\sigma_j^2) &= \IG(\tilde a_{\sigma j},\tilde b_{\sigma j}), \\
\tilde a_{\sigma j} &= a_{\sigma j}+\frac{N_j}{2}, \\
\tilde b_{\sigma j} &= b_{\sigma j}+\frac{1}{2}\E_q[\mathrm{SSE}_j].
\label{eq:vb_sigma}
\end{align}
These parameters come from collecting terms in
$\log \sigma_j^2$ and $\sigma_j^{-2}$ under \eqref{eq:vb_cavi_rule}.

\subsection{Historical Covariances in VB}
The historical covariances
\[
\{\tilde{\bm W}_t,\bm W_t^{\delta^j}\colon t=1,\dots,T,\; j=1,\dots,J\}
\]
are deterministic and therefore contribute to the state factor and ELBO only through the known
historical transition terms. There is no CAVI update for any historical covariance block.

\subsection{Forecast Lead-Specific Covariance Factors}
For each lead $k=1,\dots,K_{\max}$, define the forecast innovation
\begin{align}
\bm u_{T+k}^{(f)}:=\bm x_{T+k}^{(f)}-\bm M_{T+k}^{(f)}\bm x_{T+k-1}^{(f)}
\in\R^{d_k^{(f)}}.
\end{align}
The optimal factor for the lead-specific covariance is obtained from
\begin{align}
\log q^\star(\bm W_{T+k}^{(f)})
&=
\E_{-\bm W_{T+k}^{(f)}}\!\left[
\log p(\bm W_{T+k}^{(f)})
+\log p(\bm x_{T+k}^{(f)}\given\bm x_{T+k-1}^{(f)},\bm W_{T+k}^{(f)})
\right]
+\text{const} \nonumber\\
&=
-\frac{\nu_{T+k}^{(f)}+d_k^{(f)}+2}{2}\log|\bm W_{T+k}^{(f)}|
-\frac12\tr\!\left(
\big[\bm S_{T+k}^{(f)}+\E_q[\bm u_{T+k}^{(f)}(\bm u_{T+k}^{(f)})^\T]\big]
(\bm W_{T+k}^{(f)})^{-1}
\right)
+\text{const}.
\end{align}
Hence
\begin{align}
q(\bm W_{T+k}^{(f)})
&= \IW\!\left(
\tilde\nu_{T+k}^{(f)},
\tilde{\bm S}_{T+k}^{(f)}
\right), \\
\tilde\nu_{T+k}^{(f)}
&= \nu_{T+k}^{(f)} + 1, \\
\tilde{\bm S}_{T+k}^{(f)}
&= \bm S_{T+k}^{(f)} + \E_q[\bm u_{T+k}^{(f)}(\bm u_{T+k}^{(f)})^\T].
\label{eq:vb_W_fcast}
\end{align}
This update is exact under the mean-field factorization \eqref{eq:vb_factorization} and
does not pool information across forecast leads.

\subsection{Expectations Required Each Iteration}
\begin{itemize}
\item $\E_q[\sigma_j^{-2}]$, $\E_q[\log\sigma_j^2]$,
\item $\E_q[(\bm W_{T+k}^{(f)})^{-1}]$, $\E_q[\log|\bm W_{T+k}^{(f)}|]$ for each forecast lead $k$,
\item $\E_q[\bm x_t]$, $\E_q[\bm x_t\bm x_t^\T]$, $\E_q[\bm x_t\bm x_{t-1}^\T]$,
\item $\E_q[\mathrm{SSE}_j]$, the historical innovation moments
      $\E_q[\bm e_t^A(\bm e_t^A)^\T]$ and $\E_q[\bm e_t^{\delta,j}(\bm e_t^{\delta,j})^\T]$, and
      $\E_q[\bm u_{T+k}^{(f)}(\bm u_{T+k}^{(f)})^\T]$.
\end{itemize}
For ragged-horizon Model C, these expectations are computed on the lead-specific active
state (or the algebraically equivalent embedded fixed-dimension state) with dimension $d_k^{(f)}$.

Closed forms used in computation are:
\begin{align}
\E_q[\sigma_j^{-2}] &= \frac{\tilde a_{\sigma j}}{\tilde b_{\sigma j}},
& \E_q[\log \sigma_j^2] &= \log \tilde b_{\sigma j}-\psi(\tilde a_{\sigma j}), \label{eq:vb_sigma_moments}\\
\E_q[\bm W^{-1}] &= \tilde\nu\,\tilde{\bm S}^{-1},
& \E_q[\log|\bm W|] &= \log|\tilde{\bm S}|-\sum_{i=1}^{d}\psi\!\Big(\frac{\tilde\nu+1-i}{2}\Big)-d\log 2, \label{eq:vb_iw_moments}\\
\E_q[\bm W] &= \frac{\tilde{\bm S}}{\tilde\nu-d-1},
& &\text{when }\tilde\nu>d+1, \label{eq:vb_iw_mean}\\
\E_q[\bm x_t\bm x_t^\T] &= \bm C_t^\star+\bm m_t^\star(\bm m_t^\star)^\T,
& \E_q[\bm x_t\bm x_{t-1}^\T] &= \bm C_{t,t-1}^\star+\bm m_t^\star(\bm m_{t-1}^\star)^\T. \label{eq:vb_state_moments}
\end{align}
In \eqref{eq:vb_iw_moments}--\eqref{eq:vb_iw_mean}, $(\tilde\nu,\tilde{\bm S},d)$ denotes the
parameter triple of the lead-specific forecast inverse-Wishart factor under discussion.
Only $\E_q[\bm W^{-1}]$ and $\E_q[\log|\bm W|]$ enter the VB state update and ELBO;
$\E_q[\bm W]$ is a posterior summary and must not be substituted into the precision terms.
The cross-covariance $\bm C_{t,t-1}^\star$ is obtained from the backward smoother recursion
used to compute the Gaussian state factor.
