\section{Computational Notes and Validation Checklist}

\subsection{Observation Interface}
Implement all models through one observation-list API using tuples
$(t,n,y_{t,n},\bm h_{t,n},r_{t,n},\text{source}(n))$.
This enforces a unique mapping from each observation to its variance parameter
$\sigma_j^2$.

\subsection{Mixed Covariance Semantics}
The model uses two different covariance semantics and they must not be mixed:
\begin{itemize}
\item Historical A/B evolution covariances are deterministic time-varying outputs of the
      discount-factor construction. They are inputs to filtering, smoothing, Gibbs, VB, and ELBO
      evaluation; they are not random variables.
\item Forecast Model C evolution covariances are random lead-specific matrices
      $\bm W_{T+k}^{(f)}$, one per lead, with inverse-Wishart priors and exact Gibbs/VB updates.
\item $\lambda$ is fixed and known everywhere.
\end{itemize}

\subsection{Numerical Stability Rules}
\begin{itemize}
\item Use Cholesky solves, never explicit matrix inversion.
\item Symmetrize covariance updates: replace $\bm C\leftarrow(\bm C+\bm C^\T)/2$ after updates.
\item Floor scalar variances at a positive tolerance in implementations.
\item Historical transition covariances should be constructed before inference and passed into the
      filter/smoother with the correct time index.
\item In VB, form forecast pseudo-covariances from
      $\E_q[(\bm W_{T+k}^{(f)})^{-1}]$; do not substitute $\E_q[\bm W_{T+k}^{(f)}]$
      into the state update or ELBO.
\item If the fixed-dimension embedded forecast state is used, preserve exactness by injecting
      process noise only through the active-state subspace at each lead; equivalently, do not
      give inactive coordinates artificial innovation variance.
\end{itemize}

\subsection{Reduction Checks}
The derivations must reduce to known special cases:
\begin{itemize}
\item $J=0$ and no transfer term: standard Gaussian DLM.
\item $\bm\delta_t^j\equiv 0$: retrospective means collapse to baseline mean.
\item No forecast window ($K=0$): Model C terms vanish.
\item If all $\bm W_{T+k}^{(f)}$ are fixed rather than learned, the forecast block reduces
      to a standard time-varying linear-Gaussian state-space model with known transition covariances.
\end{itemize}

\subsection{Required Unit-Level Validations}
\begin{itemize}
\item Gaussian likelihood normalizes to one for each source.
\item IG conditional kernels match the observation-variance updates, and IW conditional kernels
      match the lead-specific forecast covariance updates $\bm W_{T+k}^{(f)}$.
\item Historical transition densities use the correct known time-varying discount-induced
      covariances $\tilde{\bm W}_t$ and $\bm W_t^{\delta^j}$ with no inferred historical
      covariance blocks.
\item Kalman/FFBS moments match brute-force Gaussian conditioning on toy systems with
      time-varying forecast transition covariances.
\item VB forecast pseudo-precisions use $\E_q[(\bm W_{T+k}^{(f)})^{-1}]$ and not
      $\E_q[\bm W_{T+k}^{(f)}]$.
\item The deterministic bridge \eqref{eq:fcast_bridge} is respected exactly in Gibbs, VB, and
      predictive calculations for the unified A+B+C model.
\item No inference routine introduces a posterior update, variational factor, or ELBO term for
      $\lambda$.
\item Reduced and augmented forecast-state implementations agree after applying the appropriate
      selection/injection maps and forecast design vectors from Section~1.
\end{itemize}

\subsection{Audit Statement}
The derivation set is intended to be implementation-complete:
joint kernels are explicit \eqref{eq:log_joint_A}--\eqref{eq:log_joint_C},
MCMC blocks are equation-linked, VB factors are derived from \eqref{eq:vb_cavi_rule},
and ELBO monitoring uses the block formulas in \eqref{eq:elbo_blocks},
\eqref{eq:elbo_init_block}--\eqref{eq:elbo_entropy_W_fcast}.
Historical A/B evolution covariances are deterministic discount-induced known quantities,
Model C uses one random forecast covariance matrix per lead,
and $\lambda$ is treated throughout as a fixed known constant rather than an inferential parameter.
Any future model extension should preserve this structure by adding
the corresponding joint, conditional, VB, and ELBO blocks before implementation.
